---
title: "01A_Exploratory Analysis of Pregnancy"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

Originally created August 15th, 2018

This document explores the pregnancy data, specifically:
- PREGHIST05
- pregbfblooddraw 

This is not combining 2007 data, but is complete based on Chris's data wrangling. For more detailed analyses, see later files. 

# Pregnancy:

## Main questions: 

 1. Who was pregnant at blood draw? 
 1. Which pregnancy number was it?
 1. Which trimester where they? 
 1. What was the outcome? (held off due to uncertainty about measurement)

# Loading packages and functions
```{r}
library(tidyverse)
library(haven)
library(visdat)
library(labelled)
library(here)


# Function for pulling out all columns with less than a certain number of missing values. 

pull_prop_nas <-function(sample.df, propor){
  x <- sample.df[ lapply( sample.df, function(x) sum(is.na(x)) / length(x) ) < propor ]
  print(x)
}


```


# Load the data

## Load the individuals for whom I have DNAm
```{r}

w.dnam <-read_csv(here("Data/Other/", "uncchdid_w_DNAm.csv"))
names(w.dnam)<-"w.dnam"

```

## Load the pregnancy blood draw data
```{r}
preghist05 <- read_dta(here("Data/2005/", "PREGHIST.dta"))  


preghist05 %>%
dim()

preghist05 %>%
  filter(uncchdid %in% w.dnam$w.dnam)%>%
  distinct(uncchdid, .keep_all = T) %>%
  names()

```

```{r}
labels <- lapply(preghist05, attr, "label")
str(labels, list.len=ncol(preghist05))

```

```{r}
# Use reprostat to isolate the individuals I'm interested in.
pregbfblooddraw <- read_dta(here("Data/Misc_2005_2009/", "pregbfblooddraw.dta"))

pregbfblooddraw


preghist05 %>%
  filter(uncchdid %in% w.dnam$w.dnam)%>%
  filter(uncchdid %in% pregbfblooddraw[pregbfblooddraw$reprostat == "0", ]$uncchdid) %>%
  distinct(uncchdid, .keep_all = T)

# One woman listed as nulliparous in reprostat appears in the preghist dataset. 22216

preghist05 %>%
  filter(uncchdid %in% w.dnam$w.dnam)%>%
  filter(uncchdid %in% pregbfblooddraw[pregbfblooddraw$reprostat == "1", ]$uncchdid) %>%
  distinct(uncchdid, .keep_all = T)

# 45 women listed as currently pregnant (reprostat says 68)

preghist05 %>%
  filter(uncchdid %in% w.dnam$w.dnam)%>%
  filter(uncchdid %in% pregbfblooddraw[pregbfblooddraw$reprostat == "2", ]$uncchdid) %>%
  distinct(uncchdid, .keep_all = T)

# 85 listed as parous are in here. Should be 86. 

preghist05 %>%
  filter(uncchdid %in% w.dnam$w.dnam)%>%
  filter(uncchdid %in% pregbfblooddraw[pregbfblooddraw$reprostat == "3", ]$uncchdid) %>%
  distinct(uncchdid, .keep_all = T)

# 63 are breastfeeding - this matches up.


# So it seems like the preghist dataset is pregnant, breastfeeding, and parous women.
# Nulliparous women are not in here, except one that slipped through (22216).

# I'm also missing a bunch of women - probably because they didn't know they were pregnant at the time. 
```

