---
title: "Exploratory Analysis of Breastfeeding"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

Exploration of breastfeeding data.   

# Breastfeeding:

## Main questions: 
 1. Who was breastfeeding during blood draw
 1. What stage of breastfeeding were they in (how long had they been breastfeeding?) When did they start? 
 1. Were they supplementing milk with formula or other foods?


## Loading packages and functions
```{r}
library(tidyverse)
library(haven)
library(visdat)
library(labelled)


# Function for pulling out all columns with less than a certain number of missing values. 

pull_prop_nas <-function(sample.df, propor){
  x <- sample.df[ lapply( sample.df, function(x) sum(is.na(x)) / length(x) ) < propor ]
  print(x)
}


```

## Load the data

### Load the individuals for whom I have DNAm
```{r}

w.dnam <-read_csv("/Users/CPR/Academic_2018/Cebu_reproductive_histories/Data/uncchdid_w_DNAm.csv")
names(w.dnam)<-"w.dnam"

```

### Load the blood draw data
```{r}
preg.blood <- read_dta("/Users/CPR/Academic_2018/Cebu_reproductive_histories/Data/2005_2009/pregbfblooddraw.dta")


preg.blood %>%
dim()

preg.blood %>%
  filter(uncchdid %in% w.dnam$w.dnam)%>%
  pull_prop_nas(0.8) %>%
  dim()

```

### Look at the labels (can also do , eval = F)
```{r}
labels <- lapply(preg.blood, attr, "label")
str(labels, list.len=ncol(preg.blood))

# Alternative way to do it...

# preg.blood.narm %>% 
#   map(~attributes(.)) %>%
#   map_chr("label", .default = NA)

```

---

# Breastfeeding

## Who was breastfeeding at the time? 

Reprostat is probably the best and perhaps only way I know of to calculate this. 

```{r}
preg.blood %>%
  filter(uncchdid %in% w.dnam$w.dnam) %>%
  filter(reprostat == "3") %>% 
  pull_prop_nas(0.99) 

```

## What stage of breastfeeding were they in (how long had they been breastfeeding)? When did they start?

```{r}
bf.dur.blood <-preg.blood %>%
  filter(uncchdid %in% w.dnam$w.dnam) %>%
  filter(reprostat == "3") %>% 
  pull_prop_nas(0.99) %>%
  select(uncchdid, pregterm, monthfromcon, dayssince, monthssince, monthssincebirth, yearssincebirth, pregcats2, yrblood, dateblood)


#  monthprg, dayprg, yearprg, maybe only apply to terminations? 
# Missing hrs1stbf etc.
```

## Were they supplementing milk with formula or other foods?

Actually all the breastfeeding women have these columns as "NA". 
In fact, all the breastfeeding columns are entirely NA. So if we're not asking these of breastfeeding women who the hell are we asking this of? 





















