---
title: "03_Merge05_09"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
    
---
Originally written November 15th or so, 2018


> This document merges and explores the 2005, 2007, and 2009 data. 
    
# Setup

---

## Setup: Options 
```{r}
knitr::opts_chunk$set(tidy = TRUE)
```


## Setup: Packages - messages hidden
```{r, warning = F, message = F}
library(tidyverse) # The tidyverse, baby
library(haven) # Used to load different datatypes, like .dat
library(readr) # Also used to read different data types
library(lubridate) # Working with dates
library(expss) # 
library(sjlabelled)
library(vcd)## used for estimating goodness of fit for poisson distribution
library(here)

```


# Load Data

---

## Load DNAm data, blooddraw data with icsex
```{r, results='hide', warning=FALSE, message=FALSE}
# Load dnam individuals 

dnam <-read_csv(here::here("Data/Other", "uncchdid_w_DNAm.csv"))
names(dnam)<-"uncchdid"
# Remove the _R1 and _R2
dnam$uncchdid <-substr(dnam$uncchdid, 1, 5)
dim(dnam)


# LOad the blood draw dates, which has the sex. Merge and keep sex for DNAm

blood.draw.dates <- read_csv(here::here("Data/Other","blood.draw.dates.csv"))[,-1]
blood.draw.dates$uncchdid <-as.character(blood.draw.dates$uncchdid)


chk.bld.draw <-left_join(dnam, blood.draw.dates, by = "uncchdid")

dnam.f <-chk.bld.draw %>% 
  filter(icsex == "0=female")
```

## Load 2005 Data
> Before and after including only women with DNAm data

```{r}
preg05 <- read_dta(here::here("Data/2005/","PREGHIST.dta"))

dim(preg05)

preg05$uncchdid <-as.character(preg05$uncchdid)
preg.dnam05 <-left_join(dnam.f, preg05, by = "uncchdid")

dim(preg.dnam05)
```

## Load 2007 Data
> Before and after including only women with DNAm data

```{r, message = F}
preg07 <- read_dta(here::here("Data/2007/Statafiles/","PREGHIST.dta"))

dim(preg07)

preg07$uncchdid <-as.character(preg07$uncchdid)
preg.dnam07 <-left_join(dnam.f, preg07, by = "uncchdid")

dim(preg.dnam07)

```

## Load 2009 Data
> Before and after including only women with DNAm data

```{r, message = F}
preg09 <- read_dta(here::here("Data/2009/Statafiles/","PREGHIST.dta"))

dim(preg09)

preg09$uncchdid <-as.character(preg09$uncchdid)
preg.dnam09 <-left_join(dnam.f, preg09, by = "uncchdid")

dim(preg.dnam09)
```

### Variables and descriptions (output not included)
> All variables in 2005, 2007 and 2009 are the same (except where year i.e. 05 has been appended!) - poor practices.

```{r}
labels <- lapply(preg09, attr, "label")
str(labels, list.len=ncol(preg09))
```

## Load 2014 
> Before and after including only women with DNAm data

```{r, message = FALSE}
preg14 <- read_dta(here::here("Data/2009_2014/Birth/corrected Stata files/","birthinfo_20141016.dta"))

dim(preg14)

# Extract the women with blood draw at T1
preg14$uncchdid <-as.character(preg14$uncchdid)

preg.dnam14 <-left_join(dnam.f, preg14, by = "uncchdid")
# 
length(unique(preg.dnam14$uncchdid))
```

### Check 2014 variables (to include change eval = T)
```{r, eval = F}
labels <- lapply(preg14, attr, "label")
str(labels, list.len=ncol(preg14))
```


# Merge 2005, 2007, 2009
> Create one file which I can then remove the duplicates and generate a tally of pregancies. 

rbind will only work where names intersect. Pick variables using intersect and bind the rows. 

## Overlapping variables for 2007, 2009
```{r}
intersect(names(preg07),names(preg09))
```
> 2007 and 2009 have much in common
> Same for 2005, 2007, and 2009, so these will merge just fine. 

## What variables overlap for 2007/2009, and 2009-14 
```{r}
intersect(intersect(names(preg07),names(preg09)), names(preg14))
```
2007/2009 and 2009-2014 (NSF) do not. 

> Merge 2005, 07, and 09.  
Chris probably already did this with 050709mergedibi.dta but I'll redo
Use as a base for other (NSF) data. 

## Pick the overlap variables - NOT INCLUDED ARE... 
```{r}
all.in <-intersect(intersect(names(preg05),names(preg07)), names(preg09))

setdiff(setdiff(names(preg05),names(preg07)), names(preg09))
```

## preg579 = 2005,2007 and 2009 from the overlap in variables
```{r}
preg579 <-rbind(preg05[,all.in], preg07[,all.in], preg09[,all.in])

```

## Include only women with DNAm
```{r}
preg579.dnam <-left_join(dnam.f, preg579, by = "uncchdid")

# View(preg579.dnam)
```



```{r}
year_neg9 <-preg579.dnam %>% 
  filter(yearprg == -9) %>% 
  pull(uncchdid)

preg579.dnam[which(preg579.dnam$uncchdid %in% year_neg9),]

# Ok, a ton of individuals have at least one of their pregnancies listed as "-9" (don't know when pregnancy will come to an end) I need a way to say, remove duplicates - but if given a duplicate, take the one where a third column is not -9 (unknown)

```

## Remove duplicate children (counted in 2005 and 2009, etc.)

Easiest solution might be to pull off all the -9, remove duplicates, reintroduce the -9, then remove duplicates again...
```{r}
pull.9 <-preg579.dnam %>% 
  filter(yearprg < 0 | is.na(yearprg))

pull.not9 <-preg579.dnam %>% 
  filter(yearprg > 0)

sum(nrow(pull.9), nrow(pull.not9))

pull.not9.nodups <-pull.not9[!duplicated(pull.not9[c("uncchdid","pregord")]),]

pull.not9.nodups_plus9 <-rbind(pull.9, pull.not9.nodups)

preg579.nodup <-pull.not9.nodups_plus9[!duplicated(pull.not9.nodups_plus9[c("uncchdid","pregord")]),]


```

```{r}
# load repro_final to see if these women were nulliparous in 2005. If not, there is a problem. If so, maybe still a problem. 
# I need to figure out WHY not pregord is in there. 

repro_final <- read_csv(here("Output/Data", "repro.final.csv"))
# repro_final was generated from my calculations of parity, pregnancy, etc. to replicate Chris's reprostat file. 
repro_final$uncchdid <-as.character(repro_final$uncchdid)

NAs <-preg579.nodup %>% 
  filter(is.na(yearprg)) %>% 
  pull(uncchdid)

repro_final[which(repro_final$uncchdid %in% 
                    NAs), ]

# Without exception, they are all nulliparous. Strongly indicative of no pregnancies. 

```
```{r}
preg579.nodup[which(preg579.nodup$uncchdid %in% NAs),]
# So all these seem to be NA because they're nulliparous. Check the individual datasets.


preg05[which(preg05$uncchdid %in% NAs),]

preg07[which(preg07$uncchdid %in% NAs),]

preg09[which(preg09$uncchdid %in% NAs),]

# Ok so all of these do NOT appear in the year pregnancy data. So we can conlude that they are nulliparous, at least up until the 2009-2014 NSF survey.
```

### How many women are NA for all pregord (parity = 0)
```{r}
# Call anyone from DNAm file with NA, 0 to count them moving forward.
preg579.nodup$pregord <- preg579.nodup$pregord %>% 
  replace_na(0)

```


### Breakdown of number of pregnancies up to 2009 + histogram
```{r message=FALSE, warning=FALSE}
# Table breakdown
preg579.nodup %>% 
  group_by(uncchdid) %>% 
  summarize(max.preg = max(pregord)) %>% 
  count(max.preg)



# Histogram of the pregnancy data
preg579.nodup %>% 
  group_by(uncchdid) %>% 
  summarize(max.preg = max(pregord)) %>% 
  ggplot(aes(x = max.preg)) +
  geom_histogram()

```


> Is there is anyone for whom pregnancies were counted twice?  
Happens if women have -9 for a pregnancy (say in 2005), and then the same pregnancy is counted but given a date in 2007/2009  

### Are there any more double-counted pregnancies?
```{r}
# Female has to have >1 pregnancy. 
# Female has to have one of them be -9 (unknown)
# One of the observations should be "still pregnant"
# Other conditions?


# Wait - if I check pregord and look for duplicates...
# Which are duplicated (first down and last up) for BOTH uncchdid and pregord.
nrow(preg579.nodup[(duplicated(preg579.nodup[c("uncchdid", "pregord")]) | duplicated(preg579.nodup[c("uncchdid", "pregord")], fromLast = TRUE)), ])
```
> Noone has duplicated pregord - no pregnancies were counted for >1 

```{r eval=FALSE, include=FALSE}

# write_csv(preg579.nodup, here::here("Output/Data", "preg579_nodup_long.csv"))

```


# SessionInfo
```{r}
sessionInfo()
```












