---
title: "05_Match_2005_pregnancies"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
    
---

Originally created: November 23, 2018

This document matches the samples from 
repro_final
preg05/07
REPRODUC.dta

The point is to characterize the inconsistencies between number of pregancies between these data sources.

Mainly, I am figuring out who changed for numbpreg (according to Chris K's wrangling), and how to incorporate or make sense of that. 


## Setup: Options 
```{r}
knitr::opts_chunk$set(tidy = TRUE)
```


## Setup: Packages - messages hidden
```{r message=F, warning=F, include=F}

library(tidyverse) # The tidyverse, baby
library(haven) # Used to load different datatypes, like .dat
library(readr) # Also used to read different data types
library(lubridate) # Working with dates
library(expss) # 
library(sjlabelled)
library(vcd)## used for estimating goodness of fit for poisson distribution
library(here)

```


```{r}
## Load my DNAm list data
dnam <- read_csv(here::here("Data/Other", "uncchdid_w_DNAm.csv"))
names(dnam) <-"uncchdid"

dnam$uncchdid <-substr(dnam$uncchdid, 1, 5)


# LOad the blood draw dates, which has the sex. Merge and keep sex for DNAm

blood.draw.dates <- read_csv(here::here("Data/Other","blood.draw.dates.csv"))[,-1]
blood.draw.dates$uncchdid <-as.character(blood.draw.dates$uncchdid)


chk.bld.draw <-left_join(dnam, blood.draw.dates, by = "uncchdid")

dnam.f <-chk.bld.draw %>% 
  filter(icsex == "0=female")
```



## Load 2005 Data
> Before and after including only women with DNAm data

```{r}
preg05 <- read_dta(here("Data/2005/","PREGHIST.dta"))

dim(preg05)

preg05$uncchdid <-as.character(preg05$uncchdid)
preg.dnam05 <-left_join(dnam.f, preg05, by = "uncchdid")

dim(preg.dnam05)
```

## Load 2007 Data
> Before and after including only women with DNAm data

```{r, message = F}
preg07 <- read_dta(here("Data/2007/Statafiles/","PREGHIST.dta"))

dim(preg07)

preg07$uncchdid <-as.character(preg07$uncchdid)
preg.dnam07 <-left_join(dnam.f, preg07, by = "uncchdid")

dim(preg.dnam07)

```
 



```{r message=FALSE, warning=FALSE}
repro_final <- read_csv(here("Output/Data", "repro.final.csv"))
# repro_final was generated from my calculations of parity, pregnancy, etc. to replicate Chris's reprostat file. 

repro_final %>% 
  group_by(pregord) %>% 
  nrow()


repro_final.parity.table <-repro_final %>% 
  group_by(pregord) %>% 
  count()

repro_final.parity.table

```

#### CWK - as used in Ryan et al. 2018
```{r}
dan.new <- read_dta(here("Data/Other", "2017-12-01 file for Calen.dta"))

dan.new$uncchdid <-as.character(dan.new$uncchdid)
dan.new <-dan.new[dan.new$uncchdid %in% dnam.f$uncchdid,]

dan.new %>% 
  group_by(numbpreg) %>% 
  nrow()


dan.parity.table <-dan.new %>% 
  group_by(numbpreg) %>% 
  count()

dan.parity.table

```
OK, but one individual has NA for numbpreg (see below)

# Sample sizes match. Both have 395 individuals (because I used uncchdid from DNAm to select those from dan.new). 
```{r}
setdiff(as.character(dan.new$uncchdid), dnam.f$uncchdid)  
setdiff(dnam.f$uncchdid, as.character(dan.new$uncchdid))
```
# Both have the same individuals. Who is different for numbpreg and numbpreg_old 
```{r}  
old.preg <-dan.new %>% 
  filter(numbpreg != numbpreg_old) %>% 
  select(uncchdid)
```


> Chris said there were 'corrections' for pregnancies after the fact. This is the difference between numbpreg_old and numbpreg.  
Looking to the file "reproduc.dta" for 2005

```{r}
repro05 <- read_dta(here("Data/2005", "REPRODUC.dta"))

repro05$uncchdid <-as.character(repro05$uncchdid)
```


```{r}
repro05.dnam <-repro05[repro05$uncchdid %in% dnam.f$uncchdid,] 

repro05[repro05$uncchdid %in% dnam.f$uncchdid,] %>%
  nrow()

```
394 makes sense. 400 women. 3 lost due to mismatch sex, 2 lost due to poor quality, 1 lost due to NA for numbpreg (see below 22980)

```{r}
setdiff(as.character(repro05.dnam$uncchdid), dnam.f$uncchdid)  
setdiff(dnam.f$uncchdid, as.character(repro05.dnam$uncchdid))
```
I'm missing 22980 from repro05
```{r}
dan.new %>% 
  filter(uncchdid == "22980") %>% 
  select(uncchdid, dnamage, numbpreg)
```
They are missing numbpreg in the Ryan et al. data too - likely did not respond or participate in the questionnaire, but maybe did in the blood collection. 

```{r}
dan.new %>% 
  filter(numbpreg != numbpreg_old) %>% 
  select(uncchdid, numbpreg, numbpreg_old)

old.preg <-dan.new %>% 
  filter(numbpreg != numbpreg_old) %>% 
  select(uncchdid)

```



> Comparing original repro05 with new version:
  Women with 0 were correct  
Three women with 1 actually had 2 (106 - 3 = 103) Check  
Two women with 2 actually had 3 (66 + 3 - 2 = 67) Check  
One woman with 4 actually had 5 (5 - 1 = 4) Check  

```{r}
repro05[repro05$uncchdid %in% dnam.f$uncchdid & repro05$uncchdid %in% old.preg$uncchdid,] %>% 
  select(uncchdid, numbpreg) %>% 
  left_join(., preg07, by = "uncchdid") %>% 
  select(uncchdid, numbpreg, pregord,  yearprg, monthprg, dayprg, pregterm) %>% 
  left_join(., preg05, by = c("uncchdid")) %>% 
  mutate(date.term = paste(yearprg.x, monthprg.x, dayprg.x, sep = "-")) %>% 
  mutate(date.hist = paste(yrpreghi, monpregh, daypregh, sep = "-")) %>% 
  select(uncchdid, numbpreg, pregord.x,  pregterm.x, date.term, date.hist, pregterm.x) %>%
  distinct() %>% 
  arrange(uncchdid)  %>% 
  as.data.frame()

```

```{r}
repro_final[repro_final$uncchdid %in% old.preg$uncchdid,] %>% 
  select(uncchdid, est.concept.date, blood.draw.date, days.bt.bld.concep, reprostat, pregord, pregterm, twins) %>% 
  arrange(uncchdid) %>% 
  as.data.frame()

```








> **21016** was pregnant at with second child blood draw. This was technically her fourth pregnancy, but two miscarriages were not counted. Pregnancy history JUST after est.concept.date.  
**21090** was pregnant with second child at blood draw. Pregnancy history just before est.concept.date.    
**21516** was pregnant with third child at blood draw. Pregnancy history was just after est.concept.date.    
**21561** XXXXXXXX was breastfeeding at blood draw. Pregnancy history was taken far earlier - THIS MIGHT BE AN ERROR  
**22093** Had a miscarriage AROUND the time of the blood draw. Pregnancy although miscarried IS included.  
**22166** Was 2 mo. pregnant at preghist, and 5 months pregnant at blood draw.








