---
title: "06_Create_2014_combined"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
  code_folding: hide

---

Here the goal is to make the 2014 dataset with all pregnancies. I merge 2005/2007/2009 with the 2009-2014 data, and pull the women with placenta data and women with pregnancies in 2009-2014.

# Setup: Options 
```{r}
knitr::opts_chunk$set(tidy = TRUE)
```


# Setup: Packages - messages hidden
```{r, warning = F, message = F}
library(tidyverse) # The tidyverse, baby
library(haven) # Used to load different datatypes, like .dat
library(readr) # Also used to read different data types
library(lubridate) # Working with dates
library(expss) # 
library(sjlabelled)
library(vcd)## used for estimating goodness of fit for poisson distribution
library(here)

```

# Load Data

## Load DNAm data, blooddraw data with icsex
```{r, results='hide', warning=FALSE, message=FALSE}
# Load dnam individuals 

dnam <-read_csv(here::here("Data/Other", "uncchdid_w_DNAm.csv"))
names(dnam)<-"uncchdid"
# Remove the _R1 and _R2
dnam$uncchdid <-substr(dnam$uncchdid, 1, 5)
dim(dnam)


# LOad the blood draw dates, which has the sex. Merge and keep sex for DNAm

blood.draw.dates <- read_csv(here("Data/Other","blood.draw.dates.csv"))[,-1]
blood.draw.dates$uncchdid <-as.character(blood.draw.dates$uncchdid)


chk.bld.draw <-left_join(dnam, blood.draw.dates, by = "uncchdid")

dnam.f <-chk.bld.draw %>% 
  filter(icsex == "0=female")
```


## 2014 Pregancy Data
```{r, message = FALSE}
preg14 <- read_dta(here::here("Data/2009_2014/Birth/corrected Stata files/","birthinfo_20141016.dta"))

dim(preg14)

# Extract the women with blood draw at T1
preg14$uncchdid <-as.character(preg14$uncchdid)

preg.dnam14 <-left_join(dnam.f, preg14, by = "uncchdid")
# 
length(unique(preg.dnam14$uncchdid))
```

### Clean 2014 data
```{r}
# Call any NSFnumb that are "NA" 0 to replace them.
preg.dnam14$nsfnumb <- preg.dnam14$nsfnumb %>% 
  replace_na(0)


preg.dnam14 %>% 
  group_by(uncchdid) %>% 
  summarize(max.nsf.preg = max(nsfnumb)) %>% 
  count(max.nsf.preg)
```

## 2005-2009 Pregnancy Data  
```{r message=FALSE, warning=FALSE}
preg579.nodup <-read_csv(here::here("Output/Data", "preg579_nodup_long.csv"))
```


# Merge 2005-2014

## What variables do they have in common?
```{r}
all.in14 <-intersect(names(preg579.nodup),names(preg.dnam14))
all.in14
```

## Make new subsets with only the variables in both
```{r}
# Also, add the inverse (variable name) of each (pregord or nsfnumb) of each to include them in the merged product. 
preg.allin <-preg579.nodup[, c(all.in14, "pregord")]
preg.nsf.allin <-preg.dnam14[, c(all.in14, "nsfnumb")]
```

## Create a new variable that has NSF or pre-NSF
```{r}
preg.allin$nsf <-"pre"
preg.allin$nsfnumb <-"NA"

preg.nsf.allin$nsf <-"nsf"
preg.nsf.allin$pregord <-"NA"

# Merge and call preg.all
preg.all2 <-rbind(preg.allin, preg.nsf.allin)
```



```{r warning=FALSE}
# Create a new variable that has the max preg for pregord.
preg.all <-preg.all2 %>% 
  arrange(uncchdid) %>% 
  group_by(uncchdid) %>% 
  mutate(max.preg.ord = max(as.numeric(pregord), na.rm = T)) %>% 
  ungroup(uncchdid) 

# I supressed the warnings that there are many missing values. I'm using pregord, which is from the 2005/7/9 data and taking the max and adding that to NSF. 

# Because all NSF data is missing this, it throws an error, but it doesn't matter because I'm only using it to generate a new variable for all the pregnancies. 
```

```{r}
preg.all$new.preg <-with(preg.all, ifelse(is.na(as.numeric(preg.all$nsfnumb)),
                                          as.numeric(pregord),
                                          as.numeric(nsfnumb)+as.numeric(max.preg.ord)))

preg.all %>% 
  select(uncchdid, pregord, max.preg.ord, nsfnumb, new.preg)
```


### Breakdown of number of pregnancies in 2009-2014 (NSF) and histogram
```{r}
preg.all %>% 
  group_by(uncchdid) %>% 
  summarize(max.all.preg = max(new.preg)) %>% 
  count(max.all.preg)

preg.all %>% 
  count(uncchdid) %>% 
  nrow()

preg.all %>% 
  group_by(uncchdid) %>% 
  summarize(max.all.preg = max(new.preg)) %>% 
  ggplot(aes(x = max.all.preg)) +
  geom_histogram()

preg.all <-preg.all %>% 
  group_by(uncchdid) %>% 
  mutate(max.all.preg = max(new.preg)) %>% 
  ungroup()

```

```{r}
preg.all %>% 
  distinct(uncchdid)
# And 395 rows. Bam!

# write_csv(preg.all, here::here("Output/Data", "preg_all_57914_long.csv"))
```

```{r}
all.nsf.fem.no0preg.maxNSF <-preg.dnam14 %>% 
  filter(nsfnumb > 0) %>%
  group_by(uncchdid) %>%
  slice(which.max(nsfnumb)) 
# write_csv(all.nsf.fem.no0preg.maxNSF, here::here("Output/Data", "all_nsf_fem_no0preg_maxNSF.csv"))

placenta.women <-preg.dnam14 %>% 
  filter(placenflag == "1") 

# write_csv(placenta.women, here::here("Output/Data", "placenta_women.csv"))
```

