---
title: "07_Extract_Targets"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
  code_folding: hide

---
1. Pull those with DNAm
1. Pull those with placenta
1. Pull those who were pregannt in 2005
1. Pull those who were breastfeeding in 2005
1. Make sure I don't have any of the mismatched IDs or otherwise excluded individuals. 
1. Figure out their pregnancy number in 2005 - if any are 'corrected' values from Chris's wrangling, account for that. 


# Setup: Options 
```{r}
knitr::opts_chunk$set(tidy = TRUE)
```


# Setup: Packages - messages hidden
```{r, warning = F, message = F}
library(tidyverse) # The tidyverse, baby
library(haven) # Used to load different datatypes, like .dat
library(readr) # Also used to read different data types
library(lubridate) # Working with dates
library(expss) # 
library(sjlabelled)
library(vcd)## used for estimating goodness of fit for poisson distribution
library(here)

```

# Pull those with DNAm

## Load DNAm data, blooddraw data with icsex
```{r, results='hide', warning=FALSE, message=FALSE}
# Load dnam individuals 

dnam <-read_csv(here::here("Data/Other", "uncchdid_w_DNAm.csv"))
names(dnam)<-"uncchdid"
# Remove the _R1 and _R2
dnam$uncchdid <-substr(dnam$uncchdid, 1, 5)
dim(dnam)


# LOad the blood draw dates, which has the sex. Merge and keep sex for DNAm

blood.draw.dates <- read_csv(here::here("Data/Other","blood.draw.dates.csv"))[,-1]
blood.draw.dates$uncchdid <-as.character(blood.draw.dates$uncchdid)


chk.bld.draw <-left_join(dnam, blood.draw.dates, by = "uncchdid")

dnam.f <-chk.bld.draw %>% 
  filter(icsex == "0=female")
```

# Pull those with placenta and the max/highest preg number in NSF study

## Load 2014 women 
...with placenta data, plus those without but the max pregnancy in the NSF.

```{r, message = FALSE}
placenta.women <-read_csv(here::here("Output/Data","placenta_women.csv"))


all.nsf.fem.no0preg.maxNSF <-read_csv(here::here("Output/Data","all_nsf_fem_no0preg_maxNSF.csv"))
```


## Load data for repro_final
```{r message=FALSE, warning=FALSE, paged.print=TRUE}
repro_final <- read_csv(here::here("Output/Data", "repro.final.csv"))
# repro_final was generated from my calculations of parity, pregnancy, etc. to replicate Chris's reprostat file. 

repro_final %>% 
  group_by(pregord) %>% 
  nrow()


repro_final.parity.table <-repro_final %>% 
  group_by(pregord) %>% 
  count()

repro_final.parity.table

```

## Pull off placenta from repro_final
```{r}
repro_final[which(repro_final$uncchdid %in% placenta.women$uncchdid),]
# Almost all of them are nulliparous in the 2005 study.
# 19 Total
# 14 nulliparous
# 1 pregnant
# 2 breastfeeding
# 2 parous
```

## Pull of remainder of NSF from repro_final
```{r}
repro_final[which(repro_final$uncchdid %in% all.nsf.fem.no0preg.maxNSF$uncchdid),] %>% 
  filter(reprostat == "pregnant") %>% 
  nrow()


repro_final[which(repro_final$uncchdid %in% all.nsf.fem.no0preg.maxNSF$uncchdid),] %>% 
  filter(reprostat == "breastfeeding") %>% 
  nrow()

```

# Pull those who were pregant in 2005 (ideally 3rd trimester)
# Pull those who were breastfeeding in 2005 (ideally first few months of BF)
```{r}
# Pull all pregnant and breastfeeding women in the NSF pool
repro_final.preg.breast.nsf_first <-repro_final[which(repro_final$uncchdid %in% all.nsf.fem.no0preg.maxNSF$uncchdid) , ] %>% filter(reprostat == "pregnant" | reprostat == "breastfeeding") 
# All the individuals in the NFS study that are pregnant or breastfeeding in 2005
nrow(repro_final.preg.breast.nsf_first)

# Pull the uncchdid for women in the placenflag pool
plac.women <-repro_final[which(repro_final$uncchdid %in% placenta.women$uncchdid),] %>% pull(uncchdid)

# Remove the placenflag pool women who overlap with the total pregant and breastfeeding pool
repro_final.preg.breast.nsf_part <-repro_final.preg.breast.nsf_first[-which(repro_final.preg.breast.nsf_first$uncchdid %in% plac.women),]
dim(repro_final.preg.breast.nsf_part)
  
# Pull all the women in the placenflag pool
repro_final.preg.breast.nsf_part2 <-repro_final[which(repro_final$uncchdid %in% placenta.women$uncchdid),]
dim(repro_final.preg.breast.nsf_part2)

# Combine all the women in the placenflag pool with the women in the pregnant and breastfeeding pool (after having removed the placenflag overlap)
repro_final.nsf_whole <-rbind(repro_final.preg.breast.nsf_part, repro_final.preg.breast.nsf_part2)
dim(repro_final.nsf_whole)

rm(repro_final.preg.breast.nsf_first, repro_final.preg.breast.nsf_part, repro_final.preg.breast.nsf_part2, plac.women)
```


# Make sure I don't have any of the mismatched IDs or otherwise excluded individuals. 
```{r}
mismatch.sex <-c("21192", "21401", "21417", "21514")
repro_final.nsf_whole[which(repro_final.nsf_whole$uncchdid %in% mismatch.sex),]
```

# Figure out their pregnancy number in 2005 - if any are 'corrected' values from Chris's wrangling, account for that. 

```{r}
dan.new <- read_dta(here("Data/Other", "2017-12-01 file for Calen.dta"))

dan.new$uncchdid <-as.character(dan.new$uncchdid)
dan.new <-dan.new[dan.new$uncchdid %in% dnam.f$uncchdid,]


dan.new %>% 
  select(uncchdid, numbpreg, numbpreg_old) %>% 
  filter(numbpreg != numbpreg_old) %>% 
  arrange(uncchdid)

bad.preg.uncchdid <-dan.new %>% 
  filter(numbpreg != numbpreg_old) %>% 
  pull(uncchdid) 

```

```{r}
repro_final.nsf_whole[which(repro_final.nsf_whole$uncchdid %in% bad.preg.uncchdid),] %>%
  select(uncchdid, pregord, pregterm, reprostat) %>% 
  arrange(uncchdid)
```

OK - almost all of them agree actually just from my first analysis in repro_final!  
21090 does `r emo::ji("+1")`  
21516 does `r emo::ji("+1")`  
22093 does `r emo::ji("+1")`    
22166 does `r emo::ji("+1")`  

21561 does not `r emo::ji("-1")`   
21016 does not `r emo::ji("-1")`  

```{r}
# What about this woman who has been counted as "2" pregnancies, but actually had 4 (2 miscarriages)
dan.new %>% 
  select(uncchdid, numbpreg, dnamageacc) %>% 
  filter(uncchdid == "21016" | uncchdid == "21561")

her.dnam <-dan.new %>% 
  filter(uncchdid == "21016") %>% 
  pull(dnamageacc) 


dan.new %>% 
  select(uncchdid, numbpreg, dnamageacc) %>% 
  ggplot2::ggplot(aes(x = dnamageacc)) +
  geom_histogram() +
  geom_vline(aes(xintercept = her.dnam, col = "red"))
```
What if I plot them all - where do they fall? 

```{r}
plot(dan.new$dnamageacc~dan.new$numbpreg)
points(2, her.dnam, col = "red", pch = 19, cex = 2) # Chris's "Corrected" Value
points(4, her.dnam, col = "blue", pch = 19, cex = 2) # "True" Value - including miscarriages
arrows(x0 = 2.1, y0 = her.dnam, x1 = 3.9, y1 = her.dnam, col = "gray", lty = 2, lwd = 4)
text(x = 4, y =  10, "21016")

points(3, -2.969330, col = "pink", pch = 19, cex = 2) # "Corrected" Value) 
points(2, -2.969330, col = "green", pch = 19, cex = 2) # "Corrected" Value)
arrows(x0 = 2.9, y0 = -2.969330, x1 = 2.1, y1 = -2.969330, col = "gray", lty = 2, lwd = 4)
text(x = 2.5, y = -5, "21561")
```

Wow - it strikes me that the original value is actually quite consistent with the CoR data.

I'm strongly inclined to keep these values. Matter of fact I should check all models with these in. I have a strong feeling that that last model will return to significance. 


```{r}
repro_final.nsf_whole$pregord <-repro_final.nsf_whole$pregord %>% 
  replace_na(0)

# write_csv(repro_final.nsf_whole, here::here("Output/Data", "repro_final_nsf_whole.csv"))
```

