---
title: "08_Pick_pregord_2005"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
  code_folding: hide
---

Created December 10th, 2018


2005: 
 * Take the pregord from repro.final.nsf
 * Date:
  - If !is.na(yearprg, monthprg, dayprg)  
    - use the blood sample date as pregterm.date
    - This will happen for all nulliparous women.
    
NSF:
 * Take the max.all.preg
 * If missing date...


```{r}
# I should have:
# 2007 data, to make sure I didn't miss anyone. 
# Remove Pregnancies that happened BEFORE blood.draw. 
# Remove Pregnancies that happened AFTER blood.draw. 
# Deal with the NA for dates on a case by case basis. 
```


# Setup: Options 
```{r}
knitr::opts_chunk$set(tidy = TRUE)
```


# Setup: Packages - messages hidden
```{r, warning=F, include=FALSE, paged.print=FALSE}
library(tidyverse) # The tidyverse, baby
library(haven) # Used to load different datatypes, like .dat
library(readr) # Also used to read different data types
library(lubridate) # Working with dates
library(expss) # 
library(sjlabelled)
library(vcd)## used for estimating goodness of fit for poisson distribution
library(here)

```

```{r}
# Created in 02_Create_reprostat.R
preg07.dnam.long.dates2 <-read_csv(here::here("Output/Data", "preghist07_dnam_long_dates_calculated.csv"))

preg07.dnam.long.dates2$uncchdid <-as.character(preg07.dnam.long.dates2$uncchdid)
names(preg07.dnam.long.dates2)
```

```{r}
preg07.dnam.long.dates <-preg07.dnam.long.dates2 %>% 
select(1,3, 9:10, 89:101, 14:15, 75)
```


Ok, some appear more than once. I have a total of 312 individuals. Where are the other 63 or so?
```{r}
  preg07.dnam.long.dates %>% 
  group_by(uncchdid) %>%
  arrange(est.concept.date) %>%   
  top_n(1, pregord) %>% 
  filter(icc.termdate < blood.draw.date) %>%
  filter(row_number() >1) %>% pull(uncchdid)
```
```{r}
preg07.dnam.long.dates %>% 
  filter(uncchdid == "22872")
```
22872 had twins.

23240 had twins, but was miscounted as having pregord 1,2 for that pregnancy. I fixed it in reprostat, but after I pulled this dataset out. Fix here:
```{r}
preg07.dnam.long.dates <-preg07.dnam.long.dates %>% 
  mutate(twins=replace(twins, uncchdid=="23240", 2)) %>% 
  mutate(pregord = replace(pregord, uncchdid == "23240", 1)) %>% 
  mutate(pregterm = replace(pregterm, uncchdid == "23240", 5))

preg07.dnam.long.dates %>% 
  filter(uncchdid == "23240")

```


> One Obs. ONLY and missing pregord - FOR SURE NULLIPAROUS - 0 pregs at blood.draw.date. 

```{r}
group_zero_atall <-preg07.dnam.long.dates %>% 
  group_by(uncchdid) %>%
  filter(n()==1) %>% 
  filter(is.na(pregord))%>% 
  ungroup()

```

> Conception Date for 1st pregnancy is AFTER blood.draw - 0 pregs at blood.draw.date.

```{r}
group_zero_before <-preg07.dnam.long.dates %>% 
  group_by(uncchdid) %>%
  arrange(est.concept.date) %>% 
  top_n(1, -pregord) %>% 
  filter(est.concept.date > blood.draw.date) %>% 
  ungroup()

```

I expect there to be 178 nulliparous women. I have:
```{r}
sum(nrow(group_zero_atall), nrow(group_zero_before))
```

> Pregnant at the time of blood.draw - that pregord is the one we want.

```{r}
group_preg_pregord <-preg07.dnam.long.dates %>% 
  filter(was.preg == TRUE)
```
None appear to be missing icc.termdate

> Not pregnant at the time BUT previously pregnant. What's that pregord?

```{r}
group_lastpreg_pregord <-preg07.dnam.long.dates[-which(preg07.dnam.long.dates$uncchdid %in%
                                                        group_preg_pregord$uncchdid),] %>% 
  group_by(uncchdid) %>%
  filter(icc.termdate < blood.draw.date) %>%
  top_n(1, pregord) %>%
  ungroup()
```


```{r}
pregs.start <-rbind(group_zero_atall, group_zero_before, group_preg_pregord, group_lastpreg_pregord)

pregs.start
```


> Let's look at those that are NOT in the currently pulled pregs.start

```{r}
acct_for <-pregs.start %>% 
  distinct(uncchdid) %>% 
  pull(uncchdid)


group_preg.2007 <-preg07.dnam.long.dates[-which(preg07.dnam.long.dates$uncchdid %in% acct_for),] 

```
All are currently pregnant WITH THEIR FIRST at the 2007 preghist. This means that they were nulliparous (0) at 2005.  Adding these guys to the nulliparous I already have brings me right up to the number of nulliparous I already calculated. 
```{r}
sum(nrow(group_zero_atall), nrow(group_zero_before), nrow(preg07.dnam.long.dates[-which(preg07.dnam.long.dates$uncchdid %in% acct_for),] 
))
```

```{r}
pregs.mid <-rbind(group_zero_atall, group_zero_before, group_preg_pregord, group_lastpreg_pregord, group_preg.2007)
nrow(pregs.mid)
```


> Who shows up > 1? 

```{r}
pregs.mid %>% 
  group_by(uncchdid) %>% 
  filter(n()>1) %>% 
  arrange(uncchdid)
```
A bunch had twins

```{r}
pregs.mid %>% 
  group_by(uncchdid) %>% 
  filter(twins != "2") %>% 
  filter(n()>1) %>% 
  arrange(uncchdid)
```

```{r}
pregs.complete <-pregs.mid %>% 
  group_by(uncchdid) %>%
  arrange(iccidnum) %>% 
  distinct(uncchdid, .keep_all = T) 

pregs.complete
```
# Mission: Accomplished!

Now just to turn many of the weird rows into 0
```{r}
# All the women who are pregnant (6 or -7) are for 2007. They should be called 0 (in 2005)                
pregs.complete %>% 
  filter(pregterm == "6" | pregterm == "-7")
                                
```

```{r}
pregs.complete %>% 
  filter(was.lact == TRUE)
```



```{r}
source(here::here("Scripts","ifelse_wrapper_function.R"))

# attach(pregs.complete)
# 
# new.reprostat <- ie(
#     i(is.na(pregord), "nulliparous"),
#     i(pregterm == "6" | pregterm == "-7", "nulliparous"),
#     i(was.preg == TRUE, "pregnant"),
#     i(was.lact == TRUE, "breastfeeding"),
#     i(is.na(was.lact) & icc.termdate < blood.draw.date, "parous"),
#     e("nulliparous")
# )
#            
           
# Could not find a way to pack the entire process of selection into a single command. Rather I'll just merge in the repro.final file where I generated it. (02_Create_reprostat.R)

reprostat.from.final <-read_csv(here::here("Output/Data", "repro.final.csv"))[c("uncchdid", "reprostat")]
reprostat.from.final$uncchdid <-as.character(reprostat.from.final$uncchdid)

reprostat05_w_pregord <-left_join(pregs.complete, reprostat.from.final, by = "uncchdid")

```

Ok, now just fix all the pregord == NA and currently pregnant (in 2007) to pregord = 0
```{r}
reprostat05_w_pregord <-reprostat05_w_pregord %>% 
  mutate(pregord_2005 = if_else(reprostat == "nulliparous" |  pregterm == "6" |  pregterm == "-7", 0, pregord)) %>% 
  mutate(term.or.draw.date = if_else(pregord_2005 == "0", blood.draw.date, 
                                     if_else(!is.na(est.concept.date), est.concept.date, icc.termdate - months(9)))) %>% 
  mutate(term.or.draw.date=replace(term.or.draw.date, uncchdid=="22645", blood.draw.date)) %>%   mutate(term.or.draw.date=replace(term.or.draw.date, uncchdid=="22924", blood.draw.date)) 
                                     
```


```{r}
# write_csv(reprostat05_w_pregord, here::here("Output/Data", "reprostat05_w_pregord.csv"))
```

