---
title: "11_Full_Sample_Size"
author: "Calen P. Ryan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide

---

Started June 17th, 2019.
This file is the new updated sample pull which has ALL individuals in the NSF survey, not only the subset originally planned. 

This expands the original question to a larger sample size. Birth number TBD

--

```{r message=F, warning=F, include=FALSE, paged.print=FALSE}
knitr::opts_chunk$set(tidy = TRUE)

library(tidyverse) # The tidyverse, baby
library(haven) # Used to load different datatypes, like .dat
library(readr) # Also used to read different data types
library(lubridate) # Working with dates
# library(expss) # 
# library(sjlabelled)
# library(vcd)## used for estimating goodness of fit for poisson distribution
library(here)
library(readxl)
library(janitor) # for tidying up excel files.

```


What I need:

 * NSF pregnancy data. Take the max nsfnumb
 * The corresponding pregnancy blood sample
 * The corresponding birth sample...for some, although I have for 124 already, more than enough. 
 
 
## NSF pregnancy data: 
First we start with the preg14 variable, based on the birthinfo_20141016.dta file and processed in 06_Create_2014_combined.Rmd


## Load DNAm data, blooddraw data with icsex
```{r, results='hide', warning=FALSE, message=FALSE}
# Load dnam individuals 

dnam <-read_csv(here::here("Data/Other", "uncchdid_w_DNAm.csv"))
names(dnam)<-"uncchdid"
# Remove the _R1 and _R2
dnam$uncchdid <-substr(dnam$uncchdid, 1, 5)
dim(dnam)


# LOad the blood draw dates, which has the sex. Merge and keep sex for DNAm

blood.draw.dates <- read_csv(here("Data/Other","blood.draw.dates.csv"))[,-1]
blood.draw.dates$uncchdid <-as.character(blood.draw.dates$uncchdid)


chk.bld.draw <-left_join(dnam, blood.draw.dates, by = "uncchdid")

dnam.f <-chk.bld.draw %>% 
  filter(icsex == "0=female")
```



```{r, message = FALSE}
preg14 <- readstata13::read.dta13(here::here("Data/2009_2014/Birth/corrected Stata files/","birthinfo_20141016.dta"))
# Note that I've used the readstata13 file in order to get the labels

dim(preg14)

# Extract the women with blood draw at T1
preg14$uncchdid <-as.character(preg14$uncchdid)

preg.dnam14 <-left_join(dnam.f, preg14, by = "uncchdid")
# 
length(unique(preg.dnam14$uncchdid))
# 502 preg14 rows, 395 with DNAm values for 2005


```

What are the labels again?
```{r}
metadata <-data.frame(attr(preg14, "names"), attr(preg14, "var.labels"))

names(metadata) <-c("variable_name", "variable_label")

metadata
```

### Clean 2014 data 

Find the max pregnancy number. 
Filter out the women who were in the 2005 sample, but did not have any pregnancies in NSF.

```{r}
# Call any NSFnumb that are "NA" 0 to replace them.
preg.dnam14$nsfnumb <- preg.dnam14$nsfnumb %>% 
  replace_na(0)


preg.dnam14 %>% 
  group_by(uncchdid) %>% 
  summarize(max.nsf.preg = max(nsfnumb)) %>% 
  count(max.nsf.preg)




preg.dnam14 %>% 
  group_by(uncchdid) %>% 
  filter(nsfnumb == max(nsfnumb)) %>% # take the maximum pregnancy of the sample to stay consistent with previous method 
  filter(nsfnumb > 0) %>% # filter out the women who were in the 2005 sample, but did not have any pregnancies in NSF.
  ungroup()
```



Barcode information has pregdbsdate and nsfpregnumber. 
```{r}
barcode_ids_nsf_picks <-read_csv(here::here("Data/Other/barcode_ids_nsf_picks.csv"))

barcode_ids_nsf_picks %>% 
  arrange(uncchdid, pregnum)
```

## Join pregnancy date for females and barcode data...
```{r}
preg.barcode <-left_join(preg.dnam14 %>% 
            group_by(uncchdid) %>% 
            filter(nsfnumb == max(nsfnumb)) %>% # take the maximum pregnancy of the sample to stay consistent with previous method 
            filter(nsfnumb > 0) %>% # filter out the women who were in the 2005 sample, but did not have any pregnancies in NSF.
            ungroup() %>% 
            select(-c(icsex.y, dayblood, monthblood, yearblood)),
          barcode_ids_nsf_picks %>% 
            sjlabelled::as_character(uncchdid), 
          by = c("uncchdid", "basewman", "basebrgy", "nsfnumb" = "pregnum"))


# Date for pregnancy termination
preg.barcode$iccterm.date <-ymd(with(preg.barcode, paste(zap_labels(yearprg), zap_labels(monthprg), zap_labels(dayprg), sep = "/")))

```

```{r}
screen_info <-read_csv(here("Data/Other/screen_anthro_data_for_birth_DBSinfo.csv"))


screen_info
```

## Create full sample. 
```{r}
names(preg.barcode)
names(screen_info)


first <-preg.barcode %>% 
  select(uncchdid, basebrgy, basewman, nsfnumb, pregdbsdate, iccterm.date, shipdatepr, barcode, specimen_id, original_bag_name, bag_number, bundle_number, card_number, icsex.x)

second <-screen_info %>% 
  select(-c(basebrgy_birth_screen, basehhno_birth_screen, basehhno_anthrop, icscreen.date) ) %>% 
  sjlabelled::as_character(uncchdid)

full.sample <-left_join(first, second, by = c("uncchdid", "basewman", "basebrgy" = "basebrgy_anthrop", "iccterm.date" = "new.preg.term.date")) %>% 
  select(uncchdid:iccterm.date, icanthro.date, time.elapsed, everything(.))
```


```{r}
full.sample.long <-full.sample %>% 
  select(uncchdid, pregdbsdate, iccterm.date, icanthro.date, nsfnumb, placenflag) %>% 
  gather(key = "date.type", "date", 2:4) %>% 
  arrange(uncchdid)
```

## Note that some IDs have > 1 value in here (344 of 340 unique)


```{r}
full.sample %>% 
  group_by(uncchdid) %>% 
  filter(n()>1)
```
Check quickly

```{r}
preg.dnam14 %>% 
  filter(uncchdid == 23267 | uncchdid == 20665)
```
Both twins.

```{r}
full.sample.long$date.type <-as.factor(full.sample.long$date.type, levels = c("pregdbsdate", "iccterm.date", "icanthro.date"))
```

```{r , fig.width = 9, fig.height= 10}
full.sample.long %>%
  ggplot(., aes(x = date, y = reorder(as.character(uncchdid), desc(date)), fill = placenflag)) +
  geom_point(aes(color = date.type))+
  scale_color_manual(name = "Sample Type", 
                     values = c("royalblue1", "palegreen3", "firebrick2"),
                     labels = c("Pregnancy DBS", "Date of Birth", "Birth DBS"))+
  theme_bw()+
  theme(legend.position = "top")+
  scale_shape_manual(values = c(21, 21, 21))+
  scale_fill_manual(values = c("pink", "yellow", "blue")) +
  labs(x = "Date of Sample", y = "uncchdid") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  #  geom_line(aes(group = uncchdid), color = "palegreen3", size=0.7, alpha = 0.5, arrow = arrow(type = "closed", angle = 20, length = unit(2, "mm")))+
  #ggrepel::geom_label_repel(full.sample.long, direction = "x", hjust = 0, mapping = aes(label = sjlabelled::as_character(date)), segment.size = 0.15, nudge_x = 4000, segment.alpha = 0.1, size = 2, fill = "white")+

```

















